Report: Complex Support Vector Detector for Large MIMO System

### 2015-09-21 Report Aug 5 2015/Report Aug 2015.tex
Report modification

\usepackage[latin1]{inputenc}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{graphicx}
%\usepackage[pdftex]{graphicx}
\usepackage{psfrag}
\usepackage{color}
\usepackage{epsfig}
%\usepackage{appendix}
%\usepackage{caption}
\usepackage{cite}
\usepackage{ifpdf}
\usepackage[cmex10]{amsmath}
\usepackage{algorithm}
\usepackage{array}
\usepackage{stfloats}
\usepackage{url}
\usepackage{fixltx2e}
\usepackage{setspace} 
\usepackage{diagbox}
\usepackage{subfigure}
\usepackage{algpseudocode}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

@@

\begin{document}
\begin{spacing}{2}
%\doublespacing
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Report}

@@

%\hfill September 17, 2014
  One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) and the limited radio frequency spectrum over a complex space-time varying environment. As the most promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years and become mature, which is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} long-term evolution (LTE)\cite{3GLTE}.  The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve bandwidth efficiency) and diversity gain (better reliability of communication link) is obtained by employing spatial domain. Large MIMO (also called Massive MIMO) is an upgrade version of conventional MIMO system, it equips   unprecedentedly hundreds of low power low price antennas at base station (BS), serving several tens of terminals simultaneously, It can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness\cite{rusek2013scaling}\cite{larsson2014massive}.

  The price paid for large MIMO system is the increasing complexities for signal processing at both transmitting and receiving end. Uplink Detector is one of the key components in large MIMO system. With orders magnitude more antennas equipped at BS, benefit and challenge coexist in designing of detection algorithms for large MIMO uplink, on the one hand, large number of receive antennas provide potential of large diversity gain, on the other hand, complexity of the algorithm becomes extremely crucial to make system practical.

@@

Suboptimal linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast}, which have good performance for low loading factor in massive MIMO system (that is the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}. In the last several years, a set of detection algorithms are proposed with complexities that is comparable with LD-OSIC and suboptimal performance can be achieved.  The local search algorithm, such as likelihood ascend searching (LAS)\cite{vardhan2008low}\cite{li2010multiple}, an theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was presented\cite{sunfamily}. Layered Tabu search algorithm presented in\cite{srinidhi2011layered} is superior to the LAS algorithms because it can move away to new searching area to avoid local minimal. Message passing detectors based on belief propagation (BF) and Gaussian Approximation (GA) \cite{goldberger2011mimo}\cite{som2011low}\cite{narasimhan2014channel}\cite{som2010improved}. Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}  and Lattice Reduction (LR) aided detectors\cite{zhou2013element}.

@@

Research and industry interest of SVM boosted since 1990s, promoted by related works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}
Moreover, the kernel based methods\cite{scholkopf2002learning} carries out nonlinear learning task by mapping input data sets into high dimensional feature space, then replacing inner product of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space. This rational is supported mathematically by Reproducing Kernel Hilbert Space (RKHS). 
Based on the same regularized risk function principle, ϵ-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.

@@

Until now, although the mathematical foundation of kernel based methods is RKHS which is defined in complex domain, the most of practitioners are dealing with real data set. In communication and signal processing area, the channel gains, signals, waveforms etc. are all represented in complex form. Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can process the complex data set purely in complex domain. The simulation of channel realization and equalization in\cite{bouboulis2013complex} demonstrate a better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernel.  
Based on this work, we construct a prototype of a complexity-performance controllable detector for large MIMO based on dual channel complex SVR. The detector can work in two parallel real SVR pipeline which can be solved independently. Moreover, only real part of kernel matrix is needed in both channel. This means a large amount of computation can be reduced.
Based on the discrete time MIMO channel model, In our regression model, this CSVR-detector
is constructed without offset, Therefore, for each real SVR without offset, in principle, only one variable is needed to be updated in each iteration, In our prototype, we propose a sequential single optimization variable searching strategy that find two optimization variable sequentially, which can approximate the optimal double optimization variables searching strategy.

@@

\section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
\subsection{Regression Model}
Suppose we are given training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{l},y_{l}))$, $l$ denotes the number of training samples, $\mathbf{x}\in \mathbb{R}^{v}$ denotes input data vector, $v$ is the number of features in $\mathbf{x}$. $y$ denotes output. The regression model (either linear or non-linear regression) is given by 
\begin{equation}
y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i\in 1\cdots l 
\label{equation1}
\end{equation} 
where $\mathbf{w}$ denotes regression coefficient vector, $\Phi(x)$ denotes the mapping of $\mathbf{x}$ to higher dimensional feature space. \ref{equation1}.

@@

\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\

@@

In \ref{primal optimization problem}, $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model. $\epsilon$ denotes the precision, if the error between estimation and real output is less than $\epsilon$, As shown in Fig \ref{epsilon-SVR}, only those data points outside the shadow part, which is called $\epsilon$ tube, contribute to cost function. $\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes risk function, the simplest risk function is $R(x)=x$, risk function is determined by the statistical distribution of noise\cite{smola2004tutorial}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$. $C\sum_{i=1}^{l}(\xi_{i}+\hat{\xi}_{i})$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.

@@

From the rationale of regularized risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $f_{estimate}(\mathbf{x})$, $c(\mathbf{x},y,f_{estimate}(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise. Assume the data samples are i.i.d. Based on Maximum Likelihood (ML) principle we want to  

@@

maximize\quad \prod_{i=1}^{l}P(y_{i}|f_{estimation}(\mathbf{x}_{i}))&=maximize\quad \prod_{i=1}^{l}P(\xi_{i})\\
&=maximize\quad \prod_{i=1}^{l}P(y_{i}-f(\mathbf{x}_{i})),

@@

maximize\quad \sum_{i=1}^{l}log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))),

@@

c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i}))=-log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))).

@@

minimize\quad  \sum_{i=1}^{l}c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i})),

@@

|x|_{\epsilon}=\left\{\begin{array}{ll}
0   &if\quad |x|<\epsilon\\
|x|-\epsilon  &otherwise\\

@@

\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x}))=\frac{1}{l}\sum_{i=1}^{l}m_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),

@@

minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x})),

@@

minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),

@@

\section{Dual Channel Complex Support Vector Regression for Large MIMO system}\label{dual channel CSVR}
 Based on discrete time model of large MIMO uplink system in (\ref{discrete time MIMO system}), in our  regression model, the training data sample at detector is $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of channel propagation matrix $\mathbf{H}$, this yields a regression task without offset $b$:  
 \begin{eqnarray}
 y_{i}=f_{true}(\mathbf{h}_{i})+n,\\
 \label{regression part1a}
 f_{true}(\mathbf{h}_{i})=\mathbf{h}_{i}\mathbf{s},\\
 \label{regression part1b}
 \end{eqnarray}
 where $f_{true}()$ denotes the underlying true function, $n$ denotes additive noise.
In this regression problem, receive symbol $y$ is the output data, $\mathbf{h}$ is input data sample, transmitted symbol vector $s$ is regression coefficients. Because the large MIMO system we consider here is complex, we employ complex support vector regression (CSVR) without offset term $b$. As shown in section \ref{Introduce epsilon SVR}, in order to derive Lagrange duality optimization formula, partial derivatives of objective function with respect to $\mathbf{w}$ and $\xi$ are needed to be calculated, in CSVR, that means take partial derivatives to risk functions which are defined in complex domain. Recently mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) is employed to solve this problem\cite{bouboulis2011extension}. First we generalize our regression model by complex RKHS, 
Let $<,>_{H}$ denotes inner product operation in real RKHS. $<,>_{\mathbb{H}}$ denotes inner products operation in complex RKHS. Assume $\mathbf{x}$, $\mathbf{y}$, $\mathbf{z}$, $j$, $k$ $\in \mathbb{C}$, complex Hilbert space has the following properties 
\newtheorem{Lemma}{Lemma}
\newtheorem{Property}{Property}
\begin{Property}
 $<\mathbf{x},\mathbf{y}>_{\mathbb{H}}=<\overline{\mathbf{y},\mathbf{x}}>_{\mathbb{H}}$
\label{CHSProperty1}
\end{Property}

@@

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \Theta^{r}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{r}_{i})\\
\nonumber
+\tilde{R}(\hat{\xi}^{r}_{i}))\\
\left\{\begin{array}{ll}
0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
\xi^{r}(\hat{\xi}^{r})\geq 0\\
\end{array}\right.
\label{complex duality real part}
\end{IEEEeqnarray}

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \Theta^{i}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\beta_{i}+\hat{\beta}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{i}_{i})\\
\nonumber
+\tilde{R}(\hat{\xi}^{i}_{i}))\\
\left\{\begin{array}{ll}
0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
\xi^{i}(\hat{\xi}^{i})\geq 0\\
\end{array}\right.
\label{complex duality imaginary part}
\end{IEEEeqnarray}

The alternate form can be written as 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \Theta^{r}=-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})+Re(\mathbf{y})^{T}(\alpha-\hat{\alpha})-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})+\tilde{R}(\hat{\xi}^{r})))\\
\left\{\begin{array}{ll}
0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
\xi^{r}(\hat{\xi}^{r})\geq 0\\
\end{array}\right.
\label{complex duality real part vectorizes}
\end{IEEEeqnarray}

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \Theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})+\tilde{R}(\hat{\xi}^{i})))\\
\left\{\begin{array}{ll}
0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
\xi^{i}(\hat{\xi}^{i})\geq 0\\
\end{array}\right.
\label{complex duality imaginary part vectorized}
\end{IEEEeqnarray}
where $(\alpha-\hat{\alpha})$, $(\beta-\hat{\beta})$,$Re(\mathbf{y})$, $Im(\mathbf{y})$ denote vectors, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$, $\mathbf{K}^{r}$ denotes the matrix consist of real  part of kernel components. Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), only the real part of kernel matrix is required for each channel. In section \ref{stopping criteria}, we will further show that from the statistic analyst of channel orthogonality (which is also named channel hardening phenomenon), the imaginary part of kernel matrix can also be omitted in stopping criteria. Therefore, in large MIMO uplink system, our CSVR-MIMO detector can save half of the cost in kernel matrix computation.    
\section{Work Set Selection and Solver}\label{WSS}
(\ref{final complex lagrange duality}) can be viewed as quadratic optimization problem, The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with large data set.

@@

maximize\quad \bigtriangledown \Theta_{S}=\Theta_{S}((\alpha_{S}+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}_{s}+\hat{\delta}_{S}\mathbf{e}_{S}))-\Theta_{S}(\alpha_{S}, \hat{\alpha}_{S}),

@@

\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+(\Phi^{r}_{S})^{T}(\delta-\hat{\delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}

@@

>>>>

\usepackage[latin1]{inputenc}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{graphicx}
%\usepackage[pdftex]{graphicx}
\usepackage{psfrag}
\usepackage{color}
\usepackage{epsfig}
%\usepackage{appendix}
%\usepackage{caption}
\usepackage{cite}
\usepackage{ifpdf}
\usepackage[cmex10]{amsmath}
\usepackage{algorithm}
\usepackage{array}
\usepackage{stfloats}
\usepackage{url}
\usepackage{fixltx2e}
\usepackage{setspace} 
\usepackage{diagbox}
\usepackage{subfigure}
\usepackage{algpseudocode}
\usepackage{multirow}
\usepackage{calc}
% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

@@

\begin{document}
\begin{spacing}{2}
%\doublespacing
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Report: Complex Support Vector Detector for Large MIMO System}

@@

%\hfill September 17, 2014
  One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) and the limited radio frequency spectrum over a complex space-time varying environment. As the most promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years and become mature, which is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} long-term evolution (LTE)\cite{3GLTE}.  The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve bandwidth efficiency) and diversity gain (better reliability of communication link) is obtained by employing spatial domain. Large MIMO (also called Massive MIMO) is an upgrade version of conventional MIMO system, it equips unprecedented hundreds of low power low price antennas at base station (BS), serving several tens of terminals simultaneously, It can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness\cite{rusek2013scaling}\cite{larsson2014massive}.

  The price paid for large MIMO system is the increasing complexities for signal processing at both transmitting and receiving end. Uplink Detector is one of the key components in large MIMO system. With orders magnitude more antennas equipped at BS, benefits and challenges coexist in designing of detection algorithms for large MIMO uplink, on the one hand, large number of receive antennas provide potential of large diversity gain, on the other hand, complexity of the algorithm becomes extremely crucial to make system practical.

@@

Suboptimal linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}. In the last several years, a set of detection algorithms are proposed with complexities that is comparable with LD-OSIC and suboptimal performance can be achieved.  The local search algorithm, such as likelihood ascend searching (LAS)\cite{vardhan2008low}\cite{li2010multiple}, an theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was presented\cite{sunfamily}. Layered Tabu search algorithm presented in\cite{srinidhi2011layered} is superior to the LAS algorithms because it can move away to new searching area to avoid local minimal. Message passing detectors based on belief propagation (BF) and Gaussian Approximation (GA) \cite{goldberger2011mimo}\cite{som2011low}\cite{narasimhan2014channel}\cite{som2010improved}. Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}  and Lattice Reduction (LR) aided detectors\cite{zhou2013element}.

@@

Research and industry interest of SVM boosted since 1990s, promoted by related works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
Moreover, the kernel based methods\cite{scholkopf2002learning} carries out nonlinear learning task by mapping input data sets into high dimensional feature space, then replacing inner product of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space. This rationale is supported mathematically by Reproducing Kernel Hilbert Space (RKHS). 
Based on the same regularized risk function principle, $\epsilon$-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.

@@

Until now, although the mathematical foundation of kernel based methods is RKHS which is defined in complex domain, the most of practitioners are dealing with real data set. However in communication and signal processing area, the channel gains, signals, waveforms etc. are all represented in complex form. Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can process the complex data set purely in complex domain. The simulation of channel realization and equalization in\cite{bouboulis2013complex} demonstrate a better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernel.  
Based on this work, we construct a prototype of a complexity-performance controllable detector for large MIMO based on dual channel complex SVR. The detector can work in two parallel real SVR pipeline which can be solved independently. Moreover, only real part of kernel matrix is needed in both channel. This means a large amount of computation can be reduced.
Based on the discrete time MIMO channel model, In our regression model, this CSVR-detector
is constructed without offset, Therefore, for each real SVR without offset, in principle, only one variable is needed to be updated in each iteration, In our prototype, we propose a sequential single optimization variable searching strategy that find two optimization variable sequentially, which can approximate the optimal double optimization variables searching strategy.

@@

\section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
\subsection{Regression Model}
Suppose we are given training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{l},y_{l}))$, $l$ denotes the number of training samples, $\mathbf{x}\in \mathbb{R}^{v}$ denotes input data vector, $v$ is the number of features in $\mathbf{x}$. $y$ denotes output. The regression model (either linear or non-linear regression) is given by 
\begin{equation}
y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i\in 1\cdots l 
\label{equation1}
\end{equation} 
where $\mathbf{w}$ denotes regression coefficient vector, $\Phi(x)$ denotes the mapping of $\mathbf{\mathbf{x}}$ to higher dimensional feature space.

@@

\min_{\mathbf{w}} \frac{1}{2}||\mathbf{w}||^{2}+C\sum_{j=1}^{l}(R(\xi_{i})+R(\hat{\xi}_{i}))\\

@@

In \ref{primal optimization problem}, $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model. $\epsilon$ denotes the precision, if the error between estimation and real output is less than $\epsilon$, As shown in Fig \ref{epsilon-SVR}, only those data points outside the shadow part, which is called $\epsilon$ tube, contribute to cost function. $\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes risk function, the simplest risk function is $R(u)=u$, risk function is determined by the statistical distribution of noise\cite{smola2004tutorial}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$. $C\sum_{i=1}^{l}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.

@@

From the rationale of regularized risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $c(\mathbf{x},y,f(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise. Assume the data samples are i.i.d. Based on Maximum Likelihood (ML) principle we want to  

@@

\max_{f()}\quad \prod_{i=1}^{l}P(y_{i}|f_{true}(\mathbf{x}_{i}))&=\max\quad \prod_{i=1}^{l}P(\xi_{i})\\
&=\max\quad \prod_{i=1}^{l}P(y_{i}-f_{true}(\mathbf{x}_{i})),

@@

maximize\quad \sum_{i=1}^{l}log(P(y_{i}-f(\mathbf{x}_{i}))),

@@

c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=-log(P(y_{i}-f(\mathbf{x}_{i}))).

@@

minimize\quad  \sum_{i=1}^{l}c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i})),

@@

|u|_{\epsilon}=\left\{\begin{array}{ll}
0   &if\quad |u|<\epsilon\\
|u|-\epsilon  &otherwise\\

@@

\tilde{c}(\mathbf{x}, y, f(\mathbf{x}))=\frac{1}{l}\sum_{i=1}^{l}m_{i}(-log(P(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))),

@@

minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f}(\mathbf{x})),

@@

minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))),

@@

\section{Dual Channel Complex Support Vector detection for Large MIMO system}\label{dual channel CSVR}
 Based on discrete time model of large MIMO uplink system in (\ref{discrete time MIMO system}), in our  regression model, the training data sample at detector is $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of channel propagation matrix $\mathbf{H}$, this yields a regression task without offset $b$:  
 \begin{eqnarray}
 y_{i}=f_{true}(\mathbf{h}_{i})+n,\\
 \label{regression part1a}
 f_{true}(\mathbf{h}_{i})=\mathbf{h}_{i}\mathbf{s},\\
 \label{regression part1b}
 \end{eqnarray}
 where $f_{true}()$ denotes the underlying true function, $n$ denotes additive noise.
In this regression problem, receive symbol $y$ is the output data, $\mathbf{h}$ is input data sample, transmitted symbol vector $s$ is regression coefficients. Because the large MIMO system we consider here is complex, we employ complex support vector regression (CSVR) without offset term $b$. As shown in section \ref{Introduce epsilon SVR}, in order to derive Lagrange duality optimization formula, partial derivatives of objective function with respect to $\mathbf{w}$ and $\xi$ are needed to be calculated, in CSVR, that means take partial derivatives to risk functions which are defined in complex domain. Recently mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) is employed to solve this problem\cite{bouboulis2011extension}. First we generalize our regression model by complex RKHS, 
Let $<,>_{H}$ denotes inner product operation in real RKHS. $<,>_{\mathbb{H}}$ denotes inner products operation in complex RKHS. Assume $\mathbf{x}$, $\mathbf{y}$, $\mathbf{z}$, $j$, $k$ $\in \mathbb{C}$, complex Hilbert space has the following properties 
\newtheorem{Lemma}{Lemma}
\newtheorem{Property}{Property}
\begin{Property}
 $<\mathbf{x},\mathbf{y}>_{\mathbb{H}}=<\overline{\mathbf{y},\mathbf{x}}>_{\mathbb{H}}$
\label{CHSProperty1}
\end{Property}

@@

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \theta^{r}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{r}_{i})\\
\nonumber
+\tilde{R}(\hat{\xi}^{r}_{i}))\\
\left\{\begin{array}{ll}
0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
\xi^{r}(\hat{\xi}^{r})\geq 0\\
\end{array}\right.
\label{complex duality real part}
\end{IEEEeqnarray}

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \theta^{i}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\beta_{i}+\hat{\beta}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{i}_{i})\\
\nonumber
+\tilde{R}(\hat{\xi}^{i}_{i}))\\
\left\{\begin{array}{ll}
0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
\xi^{i}(\hat{\xi}^{i})\geq 0\\
\end{array}\right.
\label{complex duality imaginary part}
\end{IEEEeqnarray}

The alternate form can be written as 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \theta^{r}=-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})+Re(\mathbf{y})^{T}(\alpha-\hat{\alpha})-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})+\tilde{R}(\hat{\xi}^{r})))\\
\left\{\begin{array}{ll}
0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
\xi^{r}(\hat{\xi}^{r})\geq 0\\
\end{array}\right.
\label{complex duality real part vectorizes}
\end{IEEEeqnarray}

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})+\tilde{R}(\hat{\xi}^{i})))\\
\left\{\begin{array}{ll}
0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
\xi^{i}(\hat{\xi}^{i})\geq 0\\
\end{array}\right.
\label{complex duality imaginary part vectorized}
\end{IEEEeqnarray}
where $(\alpha-\hat{\alpha})$, $(\beta-\hat{\beta})$,$Re(\mathbf{y})$, $Im(\mathbf{y})$ denote vectors, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$, $\mathbf{K}^{r}$ denotes the matrix consist of real  part of kernel components. Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), only the real part of kernel matrix is required for each channel. In section \ref{stopping criteria}, we will further show that from the statistic analyst of channel orthogonality (which is also named channel hardening phenomenon), the imaginary part of kernel matrix can also be omitted in stopping criteria. Therefore, in large MIMO uplink system, our CSVR-MIMO detector can save half of the cost in kernel matrix computation.    
\section{Work Set Selection and Solver}\label{WSS}
(\ref{final complex lagrange duality}) can be viewed as quadratic optimization problem, The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with large data set.

@@

maximize\quad \bigtriangledown \theta_{S}=\theta_{S}((\alpha+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}+\hat{\delta}_{S}\mathbf{e}_{S}))-\theta_{S}(\alpha, \hat{\alpha}),

@@

\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+(\Phi^{r}_{S})^{T}(\delta-\hat{\delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}

@@

\label{intermediate function 2b}
